Time slice analyses

### 2017-11-22 analyses/02-time-slice-analyses-Wright2017.Rmd
Analysis file for Wright 2017

```{r}
## Choose a slug
slug <- "Beck2014"

@@

## Loading the tree
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))
## Adding node labels and a root age (max tree age date)
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- max(tree.age(tree)[, 1])

@@

```{r, eval = FALSE, echo = FALSE}
## Testing data: TO REMOVE
#TG: it's just faster this way
#TG: also, I've only tested it on "Epoch" since it take ages to run, should be pipelined all right though
data(BeckLee_mat99)
data(BeckLee_tree)
data(BeckLee_ages)

morphospace <- BeckLee_mat99
tree <- BeckLee_tree
FADLAD <- BeckLee_ages

```{r, eval = TRUE, warning = FALSE}
## Run the function for Beck data
slug <- "BeckLee"

## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)
#readr::write_csv(out1, path = paste0("../outputs/age", "_", slug, ".csv"))

>>>>

```{r}
## Choose a slug
slug <- "Wright2017"

@@

## Loading the tree
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))
## Adding node labels and a root age (max tree age date)
tree <- makeNodeLabel(tree, method = "number", prefix = "n")
tree$root.time <- 485.4 # specific to Wright 2017 tree

@@

```{r, eval = TRUE, warning = FALSE}
## Ages (rarefied to 3 taxa only)
out1 <- run.all.disparity.wrapper(morphospace, tree, type = "Epoch", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances),
                                metric.name = "sum_var", rarefaction = FALSE)
#readr::write_csv(out1, path = paste0("../outputs/age", "_", slug, ".csv"))
